\huge A Usability Evaluation of Tor Launcher

### 2017-03-24 pets2017-paper/pets2017-paper.tex
Spell check.

Qualitative testing is used to gain an understanding of underlying reasons, opinions, and motivations. We use qualitative testing to develop hypotheses about why people struggle to use the interface and devlop ideas for potential design modifications to the interface.

Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into useable statistics. We use quantitative testing to quantify how people interact with the interface to uncover user patterns.

>>>>

Qualitative testing is used to gain an understanding of underlying reasons, opinions, and motivations. We use qualitative testing to develop hypotheses about why people struggle to use the interface and develop ideas for potential design modifications to the interface.

Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into usable statistics. We use quantitative testing to quantify how people interact with the interface to uncover user patterns.
